%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------
%
% NOTE: This is a TEMPLATE. The body is generated from cv/cv.yaml by
% `npm run cv:tex`. Edit the preamble/macros here to change styling; edit
% cv/cv.yaml to change content. The CONTACT / SUMMARY / EXPERIENCE / SKILLS
% markers below are replaced at generation time (and are inert LaTeX comments
% if this file is ever compiled directly).

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

% Prose paragraph between a subheading and its bullet list (label-less item).
\newcommand{\resumeProse}[1]{\item\small{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Noah Stride} \\ \vspace{1pt}
    \small +447988858546 $|$ \href{mailto:noah@noahstride.co.uk}{\underline{noah@noahstride.co.uk}} $|$ \href{https://linkedin.com/in/noah-stride}{\underline{linkedin.com/in/noah-stride}} $|$ \href{https://github.com/strideynet}{\underline{github.com/strideynet}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
I'm Noah, an engineer specialising in workload identity, authentication and authorisation — on a mission to eliminate long-lived secrets and replace them with identity. I lead Teleport's Machine \& Workload Identity product and sit on the SPIFFE Steering Committee.

\vspace{6pt}
\noindent Above all, I'm a builder who loves to stay close to the user. I take products end-to-end — from problem discovery through shipping, to scaling in production and on to helping organisations adopt them.

\vspace{6pt}
\noindent I'm not actively seeking new opportunities, but I'm open to discussing roles in workload identity or adjacent spaces — either building products in this field, or helping an organisation solve this problem from the inside.

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \filbreak
    \resumeSubheading
      {Teleport $|$ Machine \& Workload Identity Lead}{May 2022 -- Present}
      \resumeProse{I lead the Machine \& Workload Identity team, owning the product roadmap, working closely with customers and prospects to understand their problems and staying hands-on in engineering day-to-day.

\vspace{4pt}
\noindent Under my leadership, Machine \& Workload Identity has grown from a proof-of-concept feature into a product now deployed by some of the world's largest companies.}
      \resumeItemListStart
        \resumeItem{Designed and implemented technically complex functionality such as workload attestation and TPM authentication, with a focus on security and performance.}
        \resumeItem{Drove the product roadmap through close engagement with customers and prospects, joining sales calls, supporting escalations and running customer interviews. Partnered with marketing and sales to position the product and shape its messaging.}
        \resumeItem{Researched and explored emerging problem spaces in workload identity, including agentic identity, bringing insights from industry discussions in SPIFFE and WIMSE into Teleport's strategic context.}
        \resumeItem{Acted as Teleport's subject matter expert on SPIFFE and workload identity, reviewing designs and guiding implementations across the wider engineering organisation.}
        \resumeItem{Collaborated with customer organisations to build the internal case for adopting workload identity, taking into account their existing infrastructure, systems and organisational structure.}
        \resumeItem{Represented Teleport at industry conferences including KubeCon, plus webinars, blog posts and talks.}
        \resumeItem{Discovered and fixed several high- and critical-severity vulnerabilities in the Teleport codebase.}
      \resumeItemListEnd
      \resumeProse{\textit{Technologies: }Workload Identity (SPIFFE/WIMSE) $\cdot$ Identity and credentials (PKI/X.509, JWT, WIT, OIDC, OAuth2) $\cdot$ Go $\cdot$ Linux $\cdot$ Kubernetes $\cdot$ gRPC/Protobuf}

    \filbreak
    \resumeSubheading
      {SPIFFE $|$ Steering Committee Member \& Spec Maintainer}{Oct 2025 -- Present}
      \resumeProse{SPIFFE is the CNCF-graduated standard for workload identity, providing a vendor-neutral framework for issuing cryptographic identities to workloads. As a member of the Steering Committee I help govern the project and advocate for its adoption, and as a spec maintainer I refine existing specifications for clarity, review the work of fellow maintainers and author new ones (e.g. WIT-SVID, which brings the novel WIMSE WIT credential format into the SPIFFE ecosystem).

\vspace{4pt}
\noindent The role exposes me to a diversity of identity problems across the industry, from established enterprise patterns to the cutting edge of agentic identity. SPIFFE's work is critical to establishing the interoperability standards that foster a healthy ecosystem and ease adoption of workload identity.}

    \filbreak
    \resumeSubheading
      {Krystal $|$ Senior Engineer (Cloud Platform)}{Apr 2021 -- Apr 2022}
      \resumeProse{Joined as a Go specialist on a strong Ruby team building Krystal's Katapult cloud platform. Designed and implemented the Kubernetes PaaS, including an operator to provision control-plane components for customer clusters and a CCM to integrate them with the wider platform. Acted as the team's SME on Go, cloud-native technologies and containerisation, and built a bespoke deployment tool for internal container-based applications that cut maintenance and deployment overhead where Kubernetes was overkill.}
      \resumeProse{\textit{Technologies: }Go $\cdot$ Docker $\cdot$ Podman $\cdot$ Containerd $\cdot$ Kubernetes $\cdot$ gRPC}

    \filbreak
    \resumeSubheading
      {Cudo Ventures $|$ Senior Engineer (Infrastructure \& SRE)}{Dec 2020 -- Apr 2021}
      \resumeProse{Returned to Cudo to lead on SRE and operations. Owned the design, deployment and operation of on-prem Kubernetes clusters that kept infrastructure costs well below cloud equivalents, and led the wider adoption of Go across the engineering team.}
      \resumeProse{\textit{Technologies: }GCP $\cdot$ Kubernetes $\cdot$ Prometheus $\cdot$ Pulumi $\cdot$ Go $\cdot$ MySQL}

    \filbreak
    \resumeSubheading
      {WalkUp $|$ Senior Backend Engineer}{Jun 2020 -- Dec 2020}
      \resumeProse{Joined as the sole backend engineer at a pre-Series A startup hitting an inflection point in growth, owning the scaling of an event-driven microservices backend from 40,000 to over 800,000 customers per week in just three months. Diagnosed and resolved reliability and scaling issues in the pre-existing codebase while delivering new features, and mentored a junior backend engineer as the team grew.}
      \resumeProse{\textit{Technologies: }Go $\cdot$ GCP $\cdot$ Kubernetes $\cdot$ Prometheus $\cdot$ RabbitMQ $\cdot$ Redis $\cdot$ Firestore}

    \filbreak
    \resumeSubheading
      {Cudo Ventures $|$ Software Engineer}{Aug 2018 -- Jun 2020}
      \resumeProse{Joined as a junior fullstack engineer straight out of college, working across the Node.js API, Electron app and Vue web app. As the team grew, my role shifted into backend, infrastructure and distributed systems work (managing Kubernetes clusters, observability tooling and deployment mechanisms), supporting the team as Cudo first ran Go in production.}
      \resumeProse{\textit{Technologies: }Vue $\cdot$ React $\cdot$ Electron $\cdot$ JavaScript $\cdot$ TypeScript $\cdot$ Go $\cdot$ GCP $\cdot$ Kubernetes $\cdot$ Ansible}

    \filbreak
    \resumeSubheading
      {Freelancing \& Consulting $|$ Software Engineer}{Nov 2016 -- Aug 2018}
      \resumeProse{Delivered freelance projects for a variety of clients with a focus on quality solutions that met their needs (generally fullstack web applications), and consulted with other developers on scaling and deploying their projects onto cloud platforms.}
    \filbreak

  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Technical}{: Workload Identity (SPIFFE/WIMSE) $\cdot$ Identity and credentials (PKI/X.509, JWT, WIT, OIDC, OAuth2) $\cdot$ Go $\cdot$ Protobuf/gRPC $\cdot$ Linux $\cdot$ Kubernetes $\cdot$ Networking (IP, TCP, TLS and SSH) $\cdot$ Distributed systems $\cdot$ Observability (OpenTelemetry and Prometheus)} \\
     \textbf{Leadership \& Product}{: End-to-end ownership of product roadmap and execution $\cdot$ Customer interviews, support and product design $\cdot$ Incident response and management $\cdot$ Customer-facing documentation and implementation support $\cdot$ Blog posts and conference talks $\cdot$ Team leadership, engineering mentorship and hiring}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
